### 2013-07-24 0_frontmatter/abstract.tex
updated for Ian changes

Put your abstract or summary in 0\_frontmatter/abstract.tex.

>>>>

On the one hand, practical application for POLSAR data processing requires the establishment of discrimination measures
  which are to be scalar and statistically consistent.
On the other hand, these same scalar observable quantities need to be naturally representative for the high-dimensional POLSAR data.
At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.

In this thesis, the statistical behavior of the determinant of POLSAR covariance matrix is explored.
Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.

As the result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix is proposed and validated.
This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
Similar to the model for SAR intensity, this generic model for POLSAR is shown to be both multiplicative and heteroskedastic.
Consequently, logarithmic transformation is applied onto these types of data converting them into additive and homoskedastic models.
From these models, several additive measures of distance are proposed for both SAR and POLSAR data.

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative model for POLSAR generalize the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
At the same time, the benefit of the homoskedastic models is multiple-folds.
For in-experienced researchers (like this author when he started this study),
  who attempt to process either SAR or POLSAR data using existing computation algorithms
  which most of the time expect an additive and homoskedastic input,
  this thesis proposes alternative and more familiar additive and homoskedastic models
    in place of the original ones which are multiplicative and heteroskedastic.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the (POL)SAR statistical estimation framework.

%\newpage
%In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
%As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
%POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
%Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
%
%The extension from SAR to POLSAR brings about the representation issue in that:
% there exists not one, like the intensity in SAR, but many observable quantities in POLSAR.
%While different statistical models have been developed for different POLSAR observables,
% for a statistical model to be useful, scalar discrimination measures need to be derived from.
%Thus on the one hand, practical application for POLSAR data processing requires the measure to be scalar, consistent and preferably homoskedastic. 
%On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
%
%Furthermore, since POLSAR can be considered as the multi-dimensional extension of the traditional SAR, a common problem exists for both SAR and POLSAR data.
%That is: the sense of subtractive distance is seriously flawed in the original multiplicative and heteroskedastic domain of (POL)SAR data.
%The digital technologies which ranges from image processing and presentation to artificial intelligence and machine learning algorithms that are used to process (POL)SAR data, however, are linear and additive in nature.
%This linear and additive nature is manifested for example: in a large number of algorithms in the field of  computational intelligence which make use of the universal MSE as objective functions, as well as the extensive use of variance and contrast in digital image processing.
%
%Thus a solution is needed to address the dual problem of 1) figuring out scalar and representative statistical models for the multi-dimensional and inter-correlated POLSAR data and 2) arriving at consistent measures of subtractive distance for both SAR and POLSAR data, which can pave the way for further applications of existing digital-based algorithms towards (POL)SAR data.
%
%In this thesis, scalar, representative and homoskedastic measures of distances are derived for the multi-dimensional, inter-correlated and heteroskedastic (POL)SAR data.
%And their benefits are highlighted against well-known published work.
%
%Specifically, compared with other scalar statistical models for POLSAR,
%  the proposed models are representative for POLSAR data in the sense that the observable being modelled is the generalized version of the representative one-channel SAR intensity in the multidimensional case.
%Moreover, several multiplicative dis-similarity measures and additive measures of distance are derived from the proposed statistical models.
%
%And similar to the ratio in the original SAR domain, the subtractive distance in the log-transformed (POL)SAR domain is statistically consistent.
%Compared to the subtractive distance in the original domain, the PDF of the subtractive distances are not dependent on the underlying backscattering coefficient.
%And compared to the ratio in the original domain, the subtractive residual is linear in nature, which fits better with the digital image processing and presentation processes.
%This has created a number of benefits, for example: the MSE is again shown to be capable of evaluating SAR speckle filters or the consistent variance is demonstrated to be instrumental in breaking the vicious circle of SAR speckle filtering.
